LaMachine: A meta-distribution for NLP software

### 2019-01-29 docs/lamachine_clarin2018.tex
some rephrasing

LaMachine offered a convenient platform for a range of different explorations and experiments in the area of NLP and
text mining.  However, for some situations LaMachine, or rather Linux in general, was not a good fit for the audience of
the workshop: For team members who did not have experience with a non-Windows environment, LaMachine was not a suitable
or useful tool. The limit of LaMachine was also reached for members who wanted to use desktop text editors with a
graphical user interface as this is not offered by LaMachine and we did not manage to get X-forwarding working in the
Ubuntu Linux VM. After a few attempts the team gave up on resolving this issue due to time pressure. This, also
demonstrates that fine-tuning the configuration of LaMachine on certain aspects is beyond the reach of a data scientist
without system administration skills. But this certainly also applies also to the installation as a whole in the
SURFsara context, which involved things like the partitioning, formatting and mounting of (virtual) drives and setting
up user accounts on the shared VM, all of which require some system administration skills.
 %verwerkt <-- <iris> it moet nog wat beter geformuleerd worden maar je snaprt wat ik bedoel
%@iris: hebben jullie verder geen gebruik proberen te maken van de Jupyter Lab omgeving? Dat biedt in ieder geval iets
%grafisch wat via web te benaderen is?

>>>>

LaMachine offered a convenient platform for a range of different explorations and experiments in the area of NLP and
text mining.  However, for some situations LaMachine, or rather Linux in general, was not a good fit for the audience of
the workshop: For team members who did not have experience with a non-Windows environment, LaMachine was not a suitable
or useful tool. The limit of LaMachine was also reached for members who wanted to use desktop text editors with a
graphical user interface as this is not offered by LaMachine. Moreover, we did not manage to get X-forwarding working in the
Ubuntu Linux VM and after a few attempts the team gave up on resolving this issue due to time pressure. This, also
demonstrates that fine-tuning the configuration of certain aspects of LaMachine, but especially beyond LaMachine, is beyond the reach of a data scientist
without system administration skills. This certainly also applies also to the installation as a whole in the
SURFsara context, which involved things like the partitioning, formatting and mounting of (virtual) drives and setting
up user accounts on the shared VM, all of which require some system administration skills and are too context-specific
to be within the scope of LaMachine.
 %verwerkt <-- <iris> it moet nog wat beter geformuleerd worden maar je snaprt wat ik bedoel
%@iris: hebben jullie verder geen gebruik proberen te maken van de Jupyter Lab omgeving? Dat biedt in ieder geval iets
%grafisch wat via web te benaderen is?
